---
title: "Project2"
author: "Nathan Waters, Lerone Williams"
date: "Monday, February 16, 2015"
output: html_document
---

In this R Markdown document we will display and document each step of CS329e R Project 2.

Project Requirements <http://www.cs.utexas.edu/~cannata/dataVis/Projects/R%20Project%202/R%20Project%20Requirements.html>.

In the source folder 01 Data, the R script dataframes.R was created to connect to Dr. Cannata's Orcale database and generate 5 data frames using tables in the Orders Schema. The RCurl package was loaded to allow general HTTP requests and process the results returned by the Web server.


```{r}
source("../01 Data/dataframe.R", echo = TRUE)
```


```{r}
source("../01 Data/dataframe1.R", echo = TRUE)

```

```{r}
source("../02 Data Wrangling/Data Wrangling.R", echo = TRUE)
```


```{r setup, results='asis'}
library(knitr)
knit_hooks$set(webgl = hook_webgl)
```


Link to video: <http://www.lynda.com/R-tutorials/R-Statistics-Essential-Training/142447-2.html?srchtrk=index:1%0Alinktypeid:2%0Aq:R%0Apage:1%0As:relevance%0Asa:true%0Aproducttypeid:2>

```{r testgl, webgl=TRUE}
source("../03 Visualizations/plot3d.R", echo = TRUE)
```


```{r}
source("../03 Visualizations/Matrix.R", echo = TRUE)
```

