---
title: "Project2"
author: "Nathan Waters, Lerone Williams"
date: "Monday, February 16, 2015"
output: html_document
---

In this R Markdown document we will display and document each step of CS329e R Project 2.

Project Requirements <http://www.cs.utexas.edu/~cannata/dataVis/Projects/R%20Project%202/R%20Project%20Requirements.html>.

In the source folder 01 Data, the R script dataframes.R was created to connect to Dr. Cannata's Orcale database and generate a data frame from the uploaded Vocabulary.csv file. The RCurl package was loaded to allow general HTTP requests and process the results returned by the Web server.


```{r}
source("../01 Data/dataframe.R", echo = TRUE)
```

A second R script dataframes1.R was created to display the vocab data frame that was previously created in the last step. The head(), tail(), tbl_df(), glimpse(), and summary() functions were used to return subsets of this data frame. 

```{r}
source("../01 Data/dataframe1.R", echo = TRUE)

```

In this data wrangling section, several work flows are constructed using the %>% pipe operator which revealed new information about the data set.

```{r}
source("../02 Data Wrangling/Data Wrangling.R", echo = TRUE)
```

Lynda.com provides instructional videos which were utilized to create these visualizations. In particular, R Statistics Essential Training, Ch8. Charts for Three or More Variables.

Link to video: <http://www.lynda.com/R-tutorials/R-Statistics-Essential-Training/142447-2.html?srchtrk=index:1%0Alinktypeid:2%0Aq:R%0Apage:1%0As:relevance%0Asa:true%0Aproducttypeid:2>


```{r setup, results='asis'}
source("../03 Visualizations/hook.R", echo = TRUE)
```

**If you do not see a spinnable 3d plot.** 
1. Navigate to the top of the page
2. Click Open in Browser 
3. Accept the Allow blocked content warning
4. Scroll down and you should see a spinnable 3d plot of the entire Vocabulary data set.
**NOTE: This works for Windows**
```{r testgl, webgl=TRUE}
source("../03 Visualizations/plot3d.R", echo = TRUE)
```

This is a scatterplot matrix with hotgrams along the diagonal.

```{r}
source("../03 Visualizations/Matrix.R", echo = TRUE)
```

